### 2014-03-17 HowtoHowtoCapon/submission/submit1/answer/answer.tex
la2pdf commit - 2014:03:17	17:34:18	(Mon17.Mar)
la2pdf commit - 2014:03:17	17:35:16	(Mon17.Mar)

\begin{enumerate}
\qi{Equation (2) using a "broadside steering vector" - this is confusing... are the authors only steering at broadside? clearly not... do the authors pre-steer all of the elements prior to forming $\R$ so that can "focus" in a wideband sense?}
\ai{We indeed presteer all the elements. To make this clearer we have now stated it again after equation (2), and explained that a generalization is straight forward by substituting $\1$ with a steering vector.}
%
\qi{Paragraph after equation (2) mentions "spatial averaging to avoid signal cancellation" - this problem might be better identified for readers by citing the Kailath reference and using "signal cancellation due to coherent multipath".}
\ai{Thank you, both suggestions are now included.}
%
\qi{Equation 4 has second summation using index $n'$, but this index does not appear in any of the terms inside the summation.}
\ai{Good catch! Fixed.}
%
\qi{Page 2 - $\R$ is averaged over K time samples... at what rate is beamformer output produced? is $\R$ averaged using a moving window process, so that $\R[n]$ is just a rank-1 update to $\R$[n — 1] and there is one beamformer output for every input time sample?}
\ai{Actually, $\R$ is averaged over $2K+1$ time samples, this can be seen from (4) it in the text that follows. TODO}
%
\qi{Page 4, in list of three optimizations - item 3 is not self-evident, but if I understand what the authors are doing, it is described by the 1985 reference by Kailath.}
\ai{We must have conveyed this in a flawed way. We are simply implementing a text-book sliding window summation, where a start sum is computed and then this is updated with a new term for each element in $\eR$. Item 3 has now been rewritten to hopefully express this better.}
%
\qi{Page 4, last paragraph of 1) Arithmetic reduction - authors should identify that the "Minimized memory" version skips step 2) from list of three optimization, and that the "Minimized instructions" version uses all three steps... I had a hard time understanding how the three "arithmetic reduction steps" were related to the plots in Figure 5, and was puzzled about where the "minimized memory" and "minimized instruction" variants of the processing had come from. Perhaps the authors can introduce these variants more clearly and more prominently.}
\ai{The reviewer is right. This is now rewritten to be more explicit.}
%
\qi{On page 6, authors say "The bottleneck in the final design is now the in-version step, which is typically 5 times slower than the build step". Surely, this merits an explanation. What is the final design being compared with? What was the expectation? What changed? Figure 3 shows FLOPs before optimization - this shows build and inversion steps of roughly the same order of magnitude in the right half of the figure. Does Figure 3 set the expectation? Figure 5 shows "relative complexity reduction" of entire pro-cess, so there is no information on relative speed of build and inversion steps. Figure 10 shows estimated FLOPs for the two steps, but since both steps have different theoretical complexities (operations counts), and the two steps do not optimize the same way, this does not provide an expectation of the relative times.}
\qi{On page 6, authors say their implementation was improved by factor of 1.5 - 2 when run on a K20. Authors could say a few words about what a K20 is, how it differs from the Quadro 6000, that the Kepler architecture actually has features that are dramatically better for scientific computing if the code is adapted to use them (kernels can call kernels, more registers, more shared memory, ability to eliminate some host-to-GPU i/o).}
\qi{Section I says 1-2 orders of magnitude. Section IV, page 6, says 2-3 orders of magnitude.}
\qi{Reference 9 has two authors, Shan and Kailath. 11. Reference 17 seems to be the reviewed manuscript? }
\ai{Reference 9 has been corrected. }
\end{enumerate}

>>>>

\qi{Equation (2) using a "broadside steering vector" - this is confusing... are the authors only steering at broadside? clearly not... do the authors pre-steer all of the elements prior to forming $\R$ so that can "focus" in a wideband sense?}
\ai{We indeed presteer all the elements. To make this clearer we have now stated it again after equation (2), and explained that a generalization is straight forward by substituting $\1$ with a steering vector.}
\qi{Paragraph after equation (2) mentions "spatial averaging to avoid signal cancellation" - this problem might be better identified for readers by citing the Kailath reference and using "signal cancellation due to coherent multipath".}
\ai{Thank you, both suggestions are now included.}
\qi{Equation 4 has second summation using index $n'$, but this index does not appear in any of the terms inside the summation.}
\ai{Good catch! Fixed.}
\qi{Page 2 - $\R$ is averaged over K time samples... at what rate is beamformer output produced? is $\R$ averaged using a moving window process, so that $\R[n]$ is just a rank-1 update to $\R$[n — 1] and there is one beamformer output for every input time sample?}
\ai{Actually, $\R$ is averaged over $2K+1$ time samples, this can be seen from (4) it in the text that follows. TODO}
\qi{Page 4, in list of three optimizations - item 3 is not self-evident, but if I understand what the authors are doing, it is described by the 1985 reference by Kailath.}
\ai{We must have conveyed this in a flawed way. We are simply implementing a text-book sliding window summation, where a start sum is computed and then this is updated with a new term for each element in $\eR$. Item 3 has now been rewritten to hopefully express this better.}
\qi{Page 4, last paragraph of 1) Arithmetic reduction - authors should identify that the "Minimized memory" version skips step 2) from list of three optimization, and that the "Minimized instructions" version uses all three steps... I had a hard time understanding how the three "arithmetic reduction steps" were related to the plots in Figure 5, and was puzzled about where the "minimized memory" and "minimized instruction" variants of the processing had come from. Perhaps the authors can introduce these variants more clearly and more prominently.}
\ai{The reviewer is right. This is now rewritten to be more explicit.}
\qi{On page 6, authors say "The bottleneck in the final design is now the inversion step, which is typically 5 times slower than the build step". Surely, this merits an explanation. What is the final design being compared with? What was the expectation? What changed? Figure 3 shows FLOPs before optimization - this shows build and inversion steps of roughly the same order of magnitude in the right half of the figure. Does Figure 3 set the expectation? Figure 5 shows "relative complexity reduction" of entire pro-cess, so there is no information on relative speed of build and inversion steps. Figure 10 shows estimated FLOPs for the two steps, but since both steps have different theoretical complexities (operations counts), and the two steps do not optimize the same way, this does not provide an expectation of the relative times.}
\qi{On page 6, authors say their implementation was improved by factor of 1.5 - 2 when run on a K20. Authors could say a few words about what a K20 is, how it differs from the Quadro 6000, that the Kepler architecture actually has features that are dramatically better for scientific computing if the code is adapted to use them (kernels can call kernels, more registers, more shared memory, ability to eliminate some host-to-GPU i/o).}
\qi{Section I says 1-2 orders of magnitude. Section IV, page 6, says 2-3 orders of magnitude.}
\ai{Well seen. This is now corrected.}
\qi{Reference 9 has two authors, Shan and Kailath. 11. Reference 17 seems to be the reviewed manuscript?}
\ai{Reference 9 has been corrected, and reference 17 (now 18) has been updated to point to the correct article. }
